Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-15 lloveras_2020.tex
trabajando en la intro

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona. The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

\albert{In this work,} data from thre EUV bands was \albert{used:} 171, 193 and 211 \AA \ in \albert{the} case of AIA, and 171, 195 and 284 \AA \ bands in \albert{the} case of EUVI. When using data from \albert{three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of \albert{the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.

@@

Figure \ref{gradt_demt} shows frequency histograms \albert{of $\dr\Tm$} for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

@@

\begin{acks}
D.G.Ll. and C.M.C. \albert{acknowledge} CONICET doctoral \albert{fellowships} (Res. Nr. 4870) to IAFE that supported \albert{their} participation in this research. \albert{D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant XXXX to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}

\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}

>>>>

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to improve their space weather forecasting capabilities. Solar rotational tomography is currently the sole observational technique that provides an empirical 3D description of some {of the fundamental} plasma parameters of the solar corona at a global scale. Based on \diego{extreme ultraviolet} data of space borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining {DEMT} reconstructions with MHD simulations using the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework. Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the declining} phase of SC 24. The 3D tomographic and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D termodinamic structure of the inner corona as revealed by the DEMT analysis. We show in particular the existence of diverse types of temperature structures in the low and mid latitudes of the streamer belt, and that the heating energy required to keep them stable may be accounted for by Alfvén waves. We show that the latest version of the AWSoM model results agree with DEMT reconstructions to within a $\approx 20\%$ accuracy or better. We report on aspects of the AWSoM model that could be improved to better reproduce the DEMT results, in particular concerning the source region of the fast/slow solar winds.}
\end{abstract}

@@

To study the global coronal 3D structure, solar rotational tomography (SRT) proved to be a powerful tool. Based on solar rotation, allow instruments to compile a time series of images that cover the entire corona.

{Based on time-series of \diego{extreme ultraviolet (EUV)} images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the \diego{quiet-Sun low corona at a global scale.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. Using solar rotation time series of EUV images taken in channels sensitive to different temperatures, the technique allows calculation of 3D maps of electron density and temperature in the heliocentric height range $1.0\,\mrsun$ to $1.2\,\mrsun$ as summarized in Section \ref{demt}.

\diego{
A combination of the DEMT and global magnetic models has provided useful insight into the 3D thermodynamical structure of the global quiet-Sun corona. For the first time we combined DEMT with coronal magnetic field modeled by a magnetohydrodynamic (MHD) model. Using the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework, which provides a global magnetohydrodynamic (MHD) model coronal magnetic field and coronal thermodynamics,a combination of DEMT and AWSoM results 
}
We carry out a quantitatively detailed comparative DEMT analysis of the Carrington Rotation (CR)-2082 during the Solar Cycle (SC) 23/24 minimum and CR-2208 during the declining fase of SC 24. To study CR-2082 data taken by the \textit{Extreme UltraViolet Imager Behind} (EUVI-B) on board the \textit{Solar TErrestrial RElations Observatory} (STEREO) was used, while data taken by the \textit{Atmospheric Imaging Assembly instrument} (AIA), on board the \textit{Solar Dynamics Observatory} (SDO) mission was used to study CR-2208.

\diego{
Complementary to this, the coronal magnetic field of the global corona can be modeled
by means of potential field source surface (PFSS) or even magnetohydrodynamics (MHD)
models. A combination of the DEMT and global magnetic models has provided useful in-
sight into the 3D thermodynamical structure of the global quiet-Sun corona
}

\diego{El parrafo de abajo lo pondria en la seccion 2.1}
In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic grid cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM) at each volxel, a measure of the temperature distribution of the plasma contained in it. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

{In this work,} data from thre EUV bands was {used:} 171, 193 and 211 \AA \ in {the} case of AIA, and 171, 195 and 284 \AA \ bands in {the} case of EUVI. When using data from {three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.

@@

Figure \ref{gradt_demt} shows frequency histograms {of $\dr\Tm$} for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

@@

\begin{acks}
D.G.Ll. and C.M.C. {acknowledge} CONICET doctoral {fellowships} (Res. Nr. 4870) to IAFE that supported {their} participation in this research. {D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant \diego{XXXX} to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}
\\
\\
\begin{footnotesize}
 Disclosure of Potential Conflicts of Interest: The authors declare that they have no conflicts of interest.
\end{footnotesize}
\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}
